Answer to comments from the Ad-hoc review committee \\ Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-11-24 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Add the 2nd round of AdHoc for long paper

\title{Answer to comments from the Ad-hoc rewiew committee \\
 Measurement of deeply virtual Compton
scattering off Helium-4 with CLAS at Jefferson Lab}

>>>>

\title{Answer to comments from the Ad-hoc review committee \\
 Measurement of deeply virtual Compton
scattering off Helium-4 with CLAS at Jefferson Lab}
